---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/README-",
  out.width = "100%"
)
```

# nexaverser

<!-- badges: start -->
<!-- badges: end -->

The goal of nexaverser is to facilitate data science initiatives at Nexa Resources by automating the most common tasks that are commonly performed in a data science project.

## Installation

You can install the development version of nexaverser from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("octaviodeliberato/nexaverser")
```

This is a basic example which shows you how to solve a common problem:

## Data prep

```{r data-prep}
library(nexaverser)

# Import data from belt filter S033
tag_tbl <- nexaverser::fz_data

# Define target output
y <- "lb_fz_filtros033silw_zn"

# Let's see the distribution of NAs across our data
visdat::vis_miss(tag_tbl)

# Let's keep only columns with at least 2/3 of valid data ...
keep <- colMeans(!is.na(tag_tbl)) > 2/3
table(keep)

tag_imp <- tag_tbl[, keep] |>
  # ... impute missing values and ...
  nexaverser::impute_missing_values() |>
  # ... get rid of outliers
  purrr::map_df(\(x) {
    if (class(x) != "Date") {
      timetk::ts_clean_vec(x)
    } else { x }
  })

# Last but not least, let's have a look at our data
tag_imp |> dplyr::glimpse()
```

# Feature selection

```{r feature-selection}
# Now that we are happy with our prepared data, let's use `Boruta` to find the most important predictors to our model
sel_features_1 <- nexaverser::select_features_with_boruta(
  .tag_dat        = tag_imp,
  .target         = y,
  .balance        = FALSE,
  .with_tentative = FALSE,
  .return_data    = FALSE,
  .task           = "regression"
)

# 'Final' dataset
df <- tag_imp |>
  dplyr::select(dplyr::all_of(c(sel_features_1, y)))
```

The selected variables are: `r paste(sel_features_1, collapse = ", ")`. The target variable is: `r y`

## Modeling

There are many modeling techniques to choose from `{nexaverser}`. for this particular example, we will use the mighty random forest.

```{r modeling}
rf_model <- nexaverser::train_ranger_model(
  .data            = df,
  .target          = y,
  .strat           = FALSE,
  .tune            = FALSE,
  .surrogate_model = TRUE
)

rf_model[["test_plot"]]
```

Finally, the variable importance of this model can be accessed with:

```r{vip}
rf_model$model$fit$fit$fit |> vip::vip()
```
